A systematic search for transiting planets using \KT

### 2015-02-08 ms.tex
grant numbers; tense of acks

\acknowledgments
It is a pleasure to thank
\ldots\
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
B.T.M. is supported by the National Science Foundation Graduate Research
Fellowship under Grant No. DGE‐1144469.
This research made use of the NASA \project{Astrophysics Data System}.

>>>>

\acknowledgments
It is a pleasure to thank
\ldots\
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation (grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).
This research made use of the NASA \project{Astrophysics Data System}.
